Review of Assigned Readings

### 2017-12-27 documentation/documentation.tex
changes design of hardware section

\subsubsection{Hardware Setup}
(Severin's Part)

>>>>

\subsubsection{Hardware Setup}
As explained in the previous section the twitter API was used to filter tweets in realtime based on the buzzword "bitcoin". The python program was running for seven days without interruption (to be checked!!!!!!!!!!!) on a raspberry pi (rpi) which was accessed with a secure shell (SSH) connection. This approach allowed us to ensure a continuous data stream while being able to access the program output regardless anywhere and anytime. Furthermore due to a low energy consumption of the rpi the method is also the most cost efficient one compared to a personal computer or NAS Server. The following section describes the different steps that have been taken in order to setup the rpi, ssh, git and python3.\newline The following steps were conducted by using a Raspberry Pi 2, a micro SD card and Python3 and Windows 10 64Bit.

\begin{enumerate}
\item Setup of the Raspberry Pi
\begin{enumerate}
\item Burn image 2017-11-29-raspbian-stretch.zip to micro SD card available from
\begin{lstlisting}[language=bash]
https://www.raspberrypi.org/downloads/raspbian/
\end{lstlisting}
\item Boot image from micro SD card 
\item Open SSH session using PuTTY SSH client for Windows available from
\begin{lstlisting}[language=bash] 
https://www.chiark.greenend.org.uk/~sgtatham/putty/latest.html
\end{lstlisting}
\item Login to server with credentials 
\end{enumerate}

\item Update system to the newest software
\begin{enumerate}
\item Update list of applications with the command
\begin{lstlisting}[language=bash]
sudo apt-get update
\end{lstlisting}
\item Update applications with the command
\begin{lstlisting}[language=bash]
sudo apt-get upgrade
\end{lstlisting}
\end{enumerate}

\item Setup Git
\begin{enumerate}
\item Install Git using the command
\begin{lstlisting}[language=bash]
 sudo apt-get install git
\end{lstlisting}
\item Clone Git repository from
\begin{lstlisting}[language=bash] 
https://github.com/joelsonderegger/twitterbitcoin.git
\end{lstlisting}
\end{enumerate}

\item Setup Pyhton3
\begin{enumerate}
\item Install Python3 using the command: sudo apt-get install Python3 \newline
\item Install the tweepy module for python using the command
\begin{lstlisting}[language=bash]
pip install tweepy
\end{lstlisting}
\end{enumerate}

\item Collect Twitter Data
\begin{enumerate}
\item Open a new screen using the command
\begin{lstlisting}[language=bash] 
screen -S 'name' 
\end{lstlisting}
\item Start python program using the command
\begin{lstlisting}[language=bash]
python3 CollectTwitterData.py
\end{lstlisting}
\item Detach the screen to keep the program running after secure shell connection has been terminated using the commands
\begin{lstlisting}[language=bash]
Ctrl+A
Ctrl+D
\end{lstlisting}
\item Re-attach the screen to check whether the script is still running using the command
\begin{lstlisting}[language=bash]
screen -r 'name'
\end{lstlisting}
\end{enumerate}

\item Download the collected data
\begin{enumerate}
\item Install FileZilla available from
\begin{lstlisting}[language=bash] 
https://filezilla-project.org/
\end{lstlisting}
\item Connect to rpi and navigate to data location \newline
\item Download data manually \newline \newline \end{enumerate}
\end{enumerate}
In summary, this approach worked quite well and run smoothly after all bugs have been resolved from the file CollectTwitterData.py A clean setup is crucial to ensure continuous data collection over a longer period.
